Package Tests

### 2020-08-14 r-package/tests_marcus/rjava_tests.Rmd
Included R5RCore class in R5 main repository. Now, a single .jar file can be generated. Updated r5_setup function to access a single .jar file.

```{r include=FALSE}
r5_path <- "/Users/marcussaraiva/Repos/r5r/JAR/"
data_path <- "/Users/marcussaraiva/Repos/data_r5r/"

>>>>

```{r include=FALSE}
# Caminho do arquivo JAR
r5_path <- "/Users/marcussaraiva/Repos/r5r/JAR/"

#Caminho da pasta com os dados: .pbf e gtfs, ou network.dat
data_path <- "/Users/marcussaraiva/Repos/data_r5r/"
